Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-02 draft.tex
merge

@@

\begin{thm}
Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
\begin{itemize}
\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\clieu (\fg \otimes \Omega_c)$.
\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
\end{itemize}
\end{thm}

@@

@@

Let us place the locally constant factorization algebra module the $E_n$-enveloping algebra $\clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.

@@

We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
Recall, this model is given by the factorization algebra on $M$:
\begin{equation}\label{eqn:centerTFT}
\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
\end{equation}

@@

\begin{dfn}
Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
\[
F^k \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
\end{dfn}

This is a filtration of factorization algebras on $M$. 
The associated graded factorization algebra is
\[
{\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
\]
Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.

 \begin{lmm}
There is a quasi-isomorphism of commutative factorization algebras on $M$:
\[
\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) .
\]
\end{lmm}

>>>>

The operad of little $n$-disks

\brian{main thrust is to interpret this in terms of the BV / BD formalism}

@@

\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
\brian{as a corollary butson-yoo}

\begin{thm}
Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
\begin{itemize}
\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
\end{itemize}
\end{thm}

@@

\subsection{A swiss cheese model}

\brian{Review interpretation of the center as a swiss cheese algebra context of Deligne conjecture}

\begin{prp}
For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times [0,1)$.
\end{prp}

@@

Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.

@@

We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
Recall, this model is given by the factorization algebra on $M$:
\begin{equation}\label{eqn:centerTFT}
\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
\end{equation}

@@

\begin{dfn}
Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
\end{dfn}

This is a filtration of factorization algebras on $M$. 
The associated graded factorization algebra is
\[
{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
\]
Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.

 \begin{lmm}
There is a quasi-isomorphism of commutative factorization algebras on $M$:
\[
\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
\end{lmm}
